Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-27 talk/iwtc11/paper.tex
new abstract

\begin{abstract}
By introducing loop peeling into the optimization step of a tracing
jit the effect of optimizations already in place will be increased
greatly. Not only will they become able to move loop invariant code
out of loop. They will also become able to reuse results from the
previous iteration. Also, the implementation of excising optimizations
can be left almost intact as they will not have to interact much with
the loop peeling.

Several benchmarks, with few guard failures, executed on the
PyPy Python JIT show over 2
times increase in speed when loop peeling was introduced. This makes
some of them almost match optimized C performance and become over 900
times faster than CPython.
\end{abstract}

>>>>

\begin{abstract}
One of the nice properties of a tracing JIT is that many of its optimization
are simple requiring one forward pass. This is not true for loop-invariant code
motion which is a very important optimization for code with tight kernels.
In this paper we present a scheme for making simple optimizations loop-aware by
using a simple pre-processing step on the trace and not changing the
optimizations themselves. The scheme can give performance improvements of a
factor over two for PyPy's Python JIT executing simple numerical kernels
bringing the performance close to that of compiled C code.
\end{abstract}
